Tackling discrepancies in freshwater invertebrate trait databases and taxonomic resolution: Harmonising across continents and trait aggregation

### 2021-02-09 Paper/Flowchart/Flowchart_methods.tex

\documentclass[../Draft_harmonization_paper.tex]{subfiles}
\usetikzlibrary{trees,
                arrows,
                shapes.geometric,
                positioning,
                calc,
                backgrounds,
                fit,
                matrix,
                shapes.geometric}

@@

\begin{tikzpicture}
      %% Nodes
      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ DBs};
      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardized to [0-1] \\ because multiple codings used \\ throughout this database};
      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Taxa more precise than \\ family-level};

@@

      \node(conversionPerc)[intstepsnode, align = center, xshift = 0cm, yshift = -2.5cm]{Traits converted to percentages \\ and normalized to [0-1]};

@@

      %%lines
      \draw[->] (duplTaxa.east) -- (normalAUS.west);
      \draw[->] (normalAUS.east) -- (omission.west);
      \draw[->] (harmonisation.east) -- (conversionPerc.west);
      \draw[->] (conversionPerc.east) -- (traitAgg.west);
      \draw[arrow1] (traitAgg.south) -- (frameExample.north);
      \draw[->] (directAgg.south) -- (tab_direct_agg.north);
      \draw[->] (stepwiseAgg.south) -- (tab_stepwise_agg.north);
      \draw[->] (tab_stepwise_agg.south) -- (stepwiseAgg2.north);
      \draw[->] (weightedAgg.south) -- (weights.north);
      \draw[->] (weights.south) -- (weights2.north);
\end{tikzpicture}

>>>>

\documentclass[../Draft_harmonization_paper.tex]{subfiles}
\usetikzlibrary{trees,
                arrows,
                shapes.geometric,
                positioning,
                calc,
                backgrounds,
                fit,
                matrix,
                shapes.geometric,
                decorations.pathreplacing, 
                angles,
                quotes}

@@

\begin{tikzpicture}
      %% Nodes
      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ databases};
      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardised to [0 - 1] \\ because multiple codings used \\ throughout this database};
      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa less \\ precise than family-level};

@@

      \node(conversionPerc)[intstepsnode, align = center, xshift = 0cm, yshift = -2.5cm]{Traits converted to proportions \\ and normalised to [0 - 1]};

@@

      %%lines
      \draw[->] (duplTaxa.east) -- (normalAUS.west);
      \draw[->] (normalAUS.east) -- (omission.west);
      \draw[->] (harmonisation.east) -- (conversionPerc.west);
      \draw[->] (conversionPerc.east) -- (traitAgg.west);
      \draw[arrow1] (traitAgg.south) to [out=200,in=40] (frameExample.north);
      \draw[arrow1] (traitAgg.south) to [out=360,in=80] (frameExample.east);
      \draw[->] (directAgg.south) -- (tab_direct_agg.north);
      \draw[->] (stepwiseAgg.south) -- (tab_stepwise_agg.north);
      \draw[->] (tab_stepwise_agg.south) -- (stepwiseAgg2.north);
      \draw[->] (weightedAgg.south) -- (weights.north);
      \draw[->] (weights.south) -- (weights2.north);
\end{tikzpicture}
